---
title: "MachineLearning"
author: "David Mott"
date: "June 18, 2015"
output: html_document
---

#Download

All of the proper Libraries. 
```{r}
library(caret)
library(randomForest)
library(e1071)
```

Download data.  
```{r}
ftrain <- "pml-training.csv"
ftest  <- "pml-testing.csv"
if (!file.exists(ftrain)) {
  download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", ftrain)
}
if (!file.exists(ftest)) {
  download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", ftest)
}
```

Load data
```{r}
traindata <- read.csv("pml-training.csv")
testdata <- read.csv("pml-testing.csv")
```
#Cleaning and PreProcessing
```{r}
classe <- traindata$classe
traindata <- traindata[, colSums(is.na(traindata)) == 0] 
testdata <- testdata[, colSums(is.na(testdata)) == 0] 
trainRemove <- grepl("^X|timestamp|window", names(traindata))
traindata <- traindata[, !trainRemove]
traindata <- traindata[, sapply(traindata, is.numeric)]
traindata$classe <- classe
testRemove <- grepl("^X|timestamp|window", names(testdata))
testdata <- testdata[, !testRemove]
testdata <- testdata[, sapply(testdata, is.numeric)]
```

Split data into proper training and testing areas.  Split using 70/30 algorithm.  
```{r}
set.seed(91259)
train <- createDataPartition(traindata$classe, p = 0.70, list=F)
training <- traindata[train,]
testing <- traindata[-train,]
```
#Model and Output

Design a model around a Random Forest.  
```{r}
control <- trainControl(method="cv", 5)
model <- train(classe ~ ., data=training, method="rf", trControl=control)
```
Output results using a plot. 
```{r}
plot(model)
```
Show Confusion Matrix of Training data. 
```{r}
pred <- predict(model, training)
confusionMatrix(pred, training$classe)
```
Show Confusion Matrix of Testing data. 
```{r}
testpred <- predict(model, testing)
confusionMatrix(testpred, testing$classe)
```
The Final output
```{r}
testfinal <- predict(model, testdata[, -length(names(testdata))])
testfinal
```
Spit out a file per vector per Submission portion of Project.
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(testfinal)